A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2025-01-08 manuscript/manuscript.qmd
formatting minor

Statistical significance agreement: agreement between RCT and emulated trial treatment effect with regards to directionality and statistical significance.

>>>>

**Statistical significance agreement**: agreement between RCT and emulated trial treatment effect with regards to directionality and statistical significance.
